---
title: "Apercu: 02_train_set1ing_model"
author: Miguel Ángel Armengol de la Hoz
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_notebook:
    code_folding: hide
    number_sections: yes
    theme: flatly
    toc: yes
    toc_float: yes

knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = paste0(substr(inputFile,1,nchar(inputFile)-4)," ",Sys.Date(),'.html')) })
---

# Environment

```{r }
library(tidyverse)
library(dplyr)
require(foreign)
require(Hmisc)
require(reshape2)
require(caret)
require(boot)
require(pROC)
library(mlbench)
library(MLmetrics)
library(gbm)
library(xgboost)
library(oddsratio)
library(hmeasure)
library(ROCR)
```

# Random Hyperparameter Tunning

The default method for optimizing tuning parameters in train_set1 is to use a grid search. This approach is usually effective but, in cases when there are many tuning parameters, it can be inefficient. An alternative is to use a combination of grid search and racing. Another is to use a random selection of tuning parameter combinations to cover the parameter space to a lesser extent.

Using [caret](https://topepo.github.io/caret/).

_We can adress later the tuning parameters approach_

```{r}
set.seed(123)
fitControl <- trainControl(method = "repeatedcv",
                           number = 10,
                           repeats = 3,
                           classProbs = TRUE,
                           summaryFunction = twoClassSummary,
                           verboseIter = T,
                           search = "random")
```

## Random selection of tuning parameter combinations

Here we are first adressing several Machine Learning methods.
There are more methods that can be addressed [Available Models in caret::train_set1](https://rdrr.io/cran/caret/man/models.html)

```{r eval=FALSE, include=FALSE}
# defining outcome, exposures

outcome_model <- 'bact'
exposures_model <- names(train_set1)[grepl("spectrum", names(train_set1))]


outcome_and_exposure <- as.formula(
  paste( paste(outcome_model ,'~'
        , paste(exposures_model, collapse = " + ") )
  )
)

# Machine learning methods
# gbmFit_set1 <- train( outcome_and_exposure
#                 ,data = train_set1,
#                 method = "gbm",
#                 trControl = fitControl,
#                 verbose = T,
#                 metric = "ROC", ## Specify which metric to optimize
#                 task_type = "GPU"
# )
svmFit_set1 <- train( outcome_and_exposure
                ,data = train_set1,
                method = "svmRadial",
                trControl = fitControl,
                preProc = c("center", "scale"),
                tuneLength = 8,
                metric = "ROC", ## Specify which metric to optimize
                task_type = "GPU"
)
rfFit_set1 <- train( outcome_and_exposure
                ,data = train_set1,
                method = "rf",
                trControl = fitControl,
                verbose = T,
                metric = "ROC" , ## Specify which metric to optimize
                task_type = "GPU"
)
xgbFit_set1 <- train( outcome_and_exposure
                ,data = train_set1,
                method = "xgbTree",
                trControl = fitControl,
                verbose = T,
                metric = "ROC" , ## Specify which metric to optimize
                task_type = "GPU"
)

lrFit_set1 <- train( outcome_and_exposure
                ,data = train_set1,
                method = "LogitBoost",
                trControl = fitControl,
                verbose = T,
                metric = "ROC" , ## Specify which metric to optimize
                task_type = "GPU"
)

```

## Best models comprarision

```{r}
resamps <- resamples(list( #gbmFit = gbmFit_set1
                          svmFit = svmFit_set1
                          ,rfFit  = rfFit_set1
                          ,xgbFit = xgbFit_set1
                          #,nnFit = nnFit   # nn failed so we are not test_set1ing it
                          ,lrFit = lrFit_set1
                          #,gamFit = gamFit
                          ))
summary_resamps<-summary(resamps)
summary_resamps<-as.data.frame(summary_resamps$statistics)
summary_resamps
```


# Selecting the model with the best performance

```{r}
# we save the best performing model (based on its ROC) and its name
best_performing_model<-get(
  rownames(summary_resamps[which(summary_resamps$ROC.Median==max(summary_resamps$ROC.Median))]
)
)
#manually select it
best_performing_model<-rfFit_set1
best_performing_model_name<-best_performing_model$method # extracts name as string from model
```

We can see **`r best_performing_model_name`** is the model with the best performance, with a Median AUROC of **`r max(summary_resamps$ROC.Median)`**.  

Its best Random Hyperparameter Tune was:  
`r best_performing_model$bestTune`

# Evaluating the predictor on our test_set1 dataset

## Creating prediction-probabilities dataset

```{r}
prediction_probabilities<-predict(rfFit_set1, newdata = test_set1,type = "prob") # We create the probabilities dataset using our best performing model.
final_predictions<-cbind(test_Y_set1,prediction_probabilities) # we bind our prediction with the actual data
final_predictions<-rename(final_predictions, obs = test_Y_set1) # the function twoClassSummary reads the actual outcome as 'obs'
# NEEDS TO BE CHANGED FOR EVERY MODEL DEPENDING ON THE OUTCOME!!!
final_predictions['pred']<-ifelse(final_predictions$Pos > .83 # we have set the threshold in .5 this can be optimized until best performance is achieved
                                  ,'Pos','Neg'
)
# Setting proper data types
final_predictions$obs<-as.factor(final_predictions$obs)
final_predictions$pred<-as.factor(final_predictions$pred)
```

## Geting evaluation insights

```{r fig.height=13, fig.width=13}
obs.labels.01 <- relabel(final_predictions$obs)
pred.labels.01 <- relabel(final_predictions$pred)
insights_list<-HMeasure(obs.labels.01,pred.labels.01)

insights_metrics<-round(as.data.frame(insights_list$metrics),3)

# we have so many different metrics, let's select only some of them
insights_metrics<-insights_metrics%>%select(AUC, Sens,Spec, Precision,F)
#renaming metric
insights_metrics<-insights_metrics%>%rename(AUROC = AUC) 

# we transpose the data for its representation
insights_metrics<-as.data.frame(t(insights_metrics))
names(insights_metrics)<-'Percent'

insights_metrics$Percent<-insights_metrics$Percent*100

insights_metrics['Category']<-rownames(insights_metrics)
# how to order the bars
insights_metrics$Category <- factor(insights_metrics$Category
                     , levels = insights_metrics$Category)

best_performing_model_name

len <- 4
df2 <- data.frame(Category = letters[1:len], Percent = rep(0, len), 
                                 Category2 = rep("", len))
insights_metrics$Category2 <- 
 paste0(insights_metrics$Category,": ",insights_metrics$Percent,"%")

# append number to category name
insights_metrics <- rbind(insights_metrics, df2)

# set factor so it will plot in descending order 
insights_metrics$Category <-
    factor(insights_metrics$Category, 
    levels=rev(insights_metrics$Category))


ggplot(insights_metrics, aes(x = Category, y = Percent
    ,fill = Category 
    ))+ 
    geom_bar(width = 0.9, stat="identity") + 
    coord_polar(theta = "y") +
    xlab("") + ylab("") +
    ylim(c(0,100)) +
    #ggtitle(paste(best_performing_model_name,"Performing Metrics")) +
    geom_text(data = insights_metrics, hjust = 1, size = 6,
              aes(x = Category, y = 0, label = Category2)) +
    theme_minimal() +
    theme(legend.position = "none",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.line = element_blank(),
          axis.text.y = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks = element_blank())+
  scale_fill_manual(
 values=c("#e57373", "#9fa8da","#81d4fa","#80cbc4","#ffab91","#fff176","#80cbc4","#81d4fa","#e57373")
,name='', labels=c("AUROC", "Sensitivity","Specificity", "F"))

```

# Several AUROC curves

## Creating plot dataset

### svm

```{r}
prediction_probabilities_svm<-predict(svmFit_set1, newdata = test_set1, type = "prob") # We create the probabilities dataset using our best performing model.
final_predictions_svm<-cbind(test_Y_set1, prediction_probabilities_svm) # we bind our prediction with the actual data
final_predictions_svm<-rename(final_predictions_svm, obs = test_Y_set1) # the function twoClassSummary reads the actual outcome as 'obs'
# NEEDS TO BE CHANGED FOR EVERY MODEL DEPENDING ON THE OUTCOME!!!
final_predictions_svm['pred']<-ifelse(final_predictions_svm$Pos > .83 # we have set the threshold in .5 this can be optimized until best performance is achieved
                                  ,'Pos','Neg'
)
# Setting proper data types
final_predictions_svm$obs<-as.factor(final_predictions_svm$obs)
final_predictions_svm$pred<-as.factor(final_predictions_svm$pred)
```

### gbm

```{r}
prediction_probabilities_gbm<-predict(gbmFit_set1, newdata = test_set1, type = "prob") # We create the probabilities dataset using our best performing model.
final_predictions_gbm<-cbind(test_Y_set1, prediction_probabilities_gbm) # we bind our prediction with the actual data
final_predictions_gbm<-rename(final_predictions_gbm, obs = test_Y_set1) # the function twoClassSummary reads the actual outcome as 'obs'
# NEEDS TO BE CHANGED FOR EVERY MODEL DEPENDING ON THE OUTCOME!!!
final_predictions_gbm['pred']<-ifelse(final_predictions_gbm$Pos > .83 # we have set the threshold in .5 this can be optimized until best performance is achieved
                                  ,'Pos','Neg'
)
# Setting proper data types
final_predictions_gbm$obs<-as.factor(final_predictions_gbm$obs)
final_predictions_gbm$pred<-as.factor(final_predictions_gbm$pred)
```

### rf

```{r}
prediction_probabilities_rf<-predict(rfFit_set1, newdata = test_set1, type = "prob") # We create the probabilities dataset using our best performing model.
final_predictions_rf<-cbind(test_Y_set1, prediction_probabilities_rf) # we bind our prediction with the actual data
final_predictions_rf<-rename(final_predictions_rf, obs = test_Y_set1) # the function twoClassSummary reads the actual outcome as 'obs'
# NEEDS TO BE CHANGED FOR EVERY MODEL DEPENDING ON THE OUTCOME!!!
final_predictions_rf['pred']<-ifelse(final_predictions_rf$Pos > .83 # we have set the threshold in .5 this can be optimized until best performance is achieved
                                  ,'Pos','Neg'
)
# Setting proper data types
final_predictions_rf$obs<-as.factor(final_predictions_rf$obs)
final_predictions_rf$pred<-as.factor(final_predictions_rf$pred)
```

### xgb

```{r}
prediction_probabilities_xgb<-predict(xgbFit_set1, newdata = test_set1, type = "prob") # We create the probabilities dataset using our best performing model.
final_predictions_xgb<-cbind(test_Y_set1, prediction_probabilities_xgb) # we bind our prediction with the actual data
final_predictions_xgb<-rename(final_predictions_xgb, obs = test_Y_set1) # the function twoClassSummary reads the actual outcome as 'obs'
# NEEDS TO BE CHANGED FOR EVERY MODEL DEPENDING ON THE OUTCOME!!!
final_predictions_xgb['pred']<-ifelse(final_predictions_xgb$Pos > .83 # we have set the threshold in .5 this can be optimized until best performance is achieved
                                  ,'Pos','Neg'
)
# Setting proper data types
final_predictions_xgb$obs<-as.factor(final_predictions_xgb$obs)
final_predictions_xgb$pred<-as.factor(final_predictions_xgb$pred)
```

### lr

```{r}
prediction_probabilities_lr<-predict(lrFit_set1, newdata = test_set1, type = "prob") # We create the probabilities dataset using our best performing model.
final_predictions_lr<-cbind(test_Y_set1, prediction_probabilities_lr) # we bind our prediction with the actual data
final_predictions_lr<-rename(final_predictions_lr, obs = test_Y_set1) # the function twoClassSummary reads the actual outcome as 'obs'
# NEEDS TO BE CHANGED FOR EVERY MODEL DEPENDING ON THE OUTCOME!!!
final_predictions_lr['pred']<-ifelse(final_predictions_lr$Pos > .83 # we have set the threshold in .5 this can be optimized until best performance is achieved
                                  ,'Pos','Neg'
)
# Setting proper data types
final_predictions_lr$obs<-as.factor(final_predictions_lr$obs)
final_predictions_lr$pred<-as.factor(final_predictions_lr$pred)
```

## ROC Plots

```{r}
#AUC per method
auc_svm<-auc(roc(relabel(test_Y_set1),relabel(final_predictions_svm$pred) ))
auc_gbm<-auc(roc(relabel(test_Y_set1),relabel(final_predictions_gbm$pred) ))
auc_rf<-auc(roc(relabel(test_Y_set1),relabel(final_predictions_rf$pred) ))
auc_xgb<-auc(roc(relabel(test_Y_set1),relabel(final_predictions_xgb$pred) ))
auc_lr<-auc(roc(relabel(test_Y_set1),relabel(final_predictions_lr$pred) ))



# svm AUROC data
df_svm <- cbind(list(1- final_predictions_svm$Neg), list(as.numeric(final_predictions_svm$obs) - 1))
pred_svm <- prediction(df_svm[1], df_svm[2])
perf_svm <- performance(pred_svm,"tpr","fpr")

# gbm AUROC data
df_gbm <- cbind(list(1- final_predictions_gbm$Neg), list(as.numeric(final_predictions_gbm$obs) - 1))
pred_gbm <- prediction(df_gbm[1], df_gbm[2])
perf_gbm <- performance(pred_gbm,"tpr","fpr")

# rf AUROC data
df_rf <- cbind(list(1- final_predictions_rf$Neg), list(as.numeric(final_predictions_rf$obs) - 1))
pred_rf <- prediction(df_rf[1], df_rf[2])
perf_rf <- performance(pred_rf,"tpr","fpr")

# xgb AUROC data
df_xgb <- cbind(list(1- final_predictions_xgb$Neg), list(as.numeric(final_predictions_xgb$obs) - 1))
pred_xgb <- prediction(df_xgb[1], df_xgb[2])
perf_xgb <- performance(pred_xgb,"tpr","fpr")

# lr AUROC data
df_lr <- cbind(list(1- final_predictions_lr$Neg), list(as.numeric(final_predictions_lr$obs) - 1))
pred_lr <- prediction(df_lr[1], df_lr[2])
perf_lr <- performance(pred_lr,"tpr","fpr")


all_rocs<-cbind(x=perf_svm@x.values[[1]],y=perf_svm@y.values[[1]],method='SVM',auc=auc_svm)
all_rocs<-rbind(all_rocs, 
                cbind(x=perf_gbm@x.values[[1]],y=perf_gbm@y.values[[1]],method='GBM',auc=auc_gbm
                )
)
all_rocs<-rbind(all_rocs, 
                cbind(x=perf_rf@x.values[[1]],y=perf_rf@y.values[[1]],method='RF',auc=auc_rf
                )
)
all_rocs<-rbind(all_rocs, 
                cbind(x=perf_xgb@x.values[[1]],y=perf_xgb@y.values[[1]],method='XGB',auc=auc_xgb
                )
)
all_rocs<-rbind(all_rocs, 
                cbind(x=perf_lr@x.values[[1]],y=perf_lr@y.values[[1]],method='LR',auc=auc_lr
                )
)


# assigning proper type to each column so ggplot process them properly
all_rocs<-as.data.frame(all_rocs)
all_rocs$x<-as.numeric(all_rocs$x)
all_rocs$y<-as.numeric(all_rocs$y)
all_rocs$auc<-round(as.numeric(all_rocs$auc),2)
  

```

```{r fig.height=5, fig.width=5}
tiff("test.tiff", units="in", width=5, height=5, res=300)
ggplot2::ggplot(data=all_rocs ,aes(x=x, y=y, colour=paste0(method,': ',auc))) +
ggplot2::geom_line()+
  theme_classic()+
  labs(colour="Method AUROC")+
  xlab('1 - Specificity')+
  ylab('Sensitivity')+
  geom_abline(intercept = 0.00, slope = 1,linetype='dashed')+
  theme(legend.position = c(0.8, 0.2))
dev.off()
```





# Variables Importance

```{r fig.height=39, fig.width=4, message=TRUE, warning=TRUE}
ggplot(varImp(rfFit_set1, scale = T))+theme_minimal() 
dataset_1_varImp<-varImp(rfFit_set1, scale = T)
dataset_1_varImp<-as.data.frame(dataset_1_varImp[["importance"]])
dataset_1_varImp$datapoint<-rownames(dataset_1_varImp)
dataset_1_varImp_top_5<-dataset_1_varImp%>%top_n(n=5,wt=Overall)

write.xlsx(dataset_1_varImp_top_5,'nitrates_varImp_top_5.xlsx',row.names = F)
```

# Explaining the model

```{r}
dataset_1_varImp_top_5$datapoint<-paste0(dataset_1_varImp_top_5$datapoint,' + 740')
dataset_1_varImp_top_5$datapoint_num <- as.numeric(sub('^[^_]*_(\\d+).*', '\\1', dataset_1_varImp_top_5$datapoint))
```

### Plotting Important variables

```{r }
# getting the aggregated dataset ready
datasetforplot_principal_analysis<-appended_series_wide[6:336]
datasetforplot_principal_analysis<-datasetforplot_principal_analysis

datasetforplot_principal_analysis<-apply( datasetforplot_principal_analysis,2, median )
datasetforplot_principal_analysis<-as.data.frame(datasetforplot_principal_analysis)


xmax<-nrow(datasetforplot_principal_analysis)-1
datasetforplot_principal_analysis$x<-c(0:xmax)

datasetforplot_principal_analysis<-rename(datasetforplot_principal_analysis, y = datasetforplot_principal_analysis)

# crating dataset with annotation
notes<-data.frame(position=c(dataset_1_varImp_top_5$datapoint_num),
                      text=c(as.character(dataset_1_varImp_top_5$datapoint_num))
)

ggplot(data = datasetforplot_principal_analysis, mapping = aes(x = x, y = y)) +
  geom_line()+
  xlim(175, 250)+
  xlab('Spectrum')+
  ylab('Absorbance')+
  ggtitle("Bacteria Nitrates Prediction Datapoints")+
  geom_vline(data=notes, mapping=aes(xintercept=position), color="grey44",linetype="dotted") +
  geom_text(data=notes, mapping=aes(x=position, y=0, label=text), size=3, angle=90, vjust=-0.4, hjust=0)+
  theme_minimal()



```

